PANCHANGE_variable_creation

### 2020-11-09 PANCHANGE_analysis.Rmd

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

>>>>

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
# GAD prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r gad model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_estimates)
gad_prepan_model1b_explan_estimates

# Regression diagnostic statistics
gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "gad.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(gad_prepan_model1b_explan_reg_stats)
gad_prepan_model1b_explan_reg_stats
```
##KT

### 2020-11-09 PANCHANGE_variable_creation.Rmd

```{r Save four cohorts as rds file}
saveRDS(object = dat, file = paste0(data_path, "/four_cohorts_variables.rds"))
```

>>>>

Creating date variables for subset of participants dependent on when they signed up to GLAD (prepan)
```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
# Date of 3 months prior to the 1st of March
date_3months_prior_march_1st <- as.POSIXct("2019-12-01")

# Date of 6 months prior to the 1st of March
date_6months_prior_march_1st <- as.POSIXct("2019-09-01")

# Date of 9 months prior to the 1st of March
date_9months_prior_march_1st <- as.POSIXct("2019-06-01")
```

```{r subset of participants who signed up in 3 months prior to pandemic}
dat <- dat %>%
  mutate(
    prepandemic_3_months_numeric =
      if_else(
        startDate.prepandemic > date_3months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
        prepandemic_march_1_numeric == 1, #participant sign up before pandemic began (March 1st)
        true = 1, # Participant signed up after December 1st 
        false = 0, # Participant signed up before December 1st
        missing = NA_real_
      )
  )

dat <- dat %>%
  mutate(
    prepandemic_3_months =
      recode_factor(
        prepandemic_3_months_numeric,
        "0" = "Sign up before 01 December",
        "1" = "Sign up after 01 December"
      )
  )

dat %>%
  freq(prepandemic_3_months)
```

```{r subset of participants who signed up in 6 months prior to pandemic}
dat <- dat %>%
  mutate(
    prepandemic_6_months_numeric =
      if_else(
        startDate.prepandemic > date_6months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
        prepandemic_march_1_numeric == 1, #participant did not sign up after pandemic began (March 1st)
        true = 1, # Participant signed up after September 1st 
        false = 0, # Participant signed up before September 1st
        missing = NA_real_
      )
  )

dat <- dat %>%
  mutate(
    prepandemic_6_months =
      recode_factor(
        prepandemic_6_months_numeric,
        "1" = "Sign up after 01 September",
        "0" = "Sign up before 01 September"
      )
  )

dat %>%
  freq(prepandemic_6_months)
```

```{r subset of participants who signed up in 9 months prior to pandemic}
dat <- dat %>%
  mutate(
    prepandemic_9_months_numeric =
      if_else(
        startDate.prepandemic > date_9months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
        prepandemic_march_1_numeric == 1, #participant did not sign up after pandemic began (March 1st)
        true = 1, # Participant signed up after June 1st 
        false = 0, # Participant signed up before June 1st
        missing = NA_real_
      )
  )

dat <- dat %>%
  mutate(
    prepandemic_9_months =
      recode_factor(
        prepandemic_9_months_numeric,
        "1" = "Sign up after 01 June",
        "0" = "Sign up before 01 June"
      )
  )

dat %>%
  freq(prepandemic_9_months)
```

##Export data
```{r Save four cohorts as rds file}
saveRDS(object = dat, file = paste0(data_path, "/four_cohorts_variables.rds"))
```
